{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex

	\paragraph{Larger Range for the Number of Specifications for FPCR}
	\vspace{-0.2cm}

	\paragraph{Input from Physics Analysis}
	\vspace{-0.2cm}

>>>>

	\paragraph{Larger Range for the Number of Specifications for FPCR}
	As alluded to before, the chosen specifications for the number of principal components and the number of basis functions that are used for FPCR might be insufficient to obtain a full picture of the performance of this procedure when combined with smoothing using basis truncation. It would therefore be interesting to focus more attention on this aspect of the paper in a future extension to explore a broader array of possible specifications which might allow the derivation of more detailed insights.
	\vspace{-0.2cm}

	\paragraph{Input from Physics}
	It would be interesting to combine the purely mathematical findings of this paper with theoretical expertise from the field of physics as this could inform the choice of models and be conducive to a more meaningful interpretation of estimates. For example, specific parts of the NIR spectrum can possibly be liked to specific molecules associated with a high predictive power for the octane value. This could guide, for example, the construction of a B-spline basis that focuses on the relevant parts of the spectrum by using a vector of knots founded by field expertise. Alternatively, it could be used to link specific principal components to compounds which would be interesting for the interpretation of estimates.
	\vspace{-0.2cm}
